Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-19 paper/paper.tex
Add subsection on steps to reproduce correlation

A Welch T Test was computed to test the difference between tickets with attachments (i.e. all categories 
shown in the graph and those without attachments. The analysis revealed significant difference with 
\emph{p} < 0.01 with an average of \emph{X <change this>} for tickets with attachments and an average of 
\emph{Y <change this>} for tickets without attachments.

>>>>

Steps to reproduce are a means of specifying to the developers what actions they need to undergo in order 
to reproduce a certain bug. They can take various forms, but as Jira uses a wiki style markdown format for 
their description and comments fields, they can be inserted as a bullet point list which can be easily 
extracted with a regular expression.

Figure \ref{steps} shows the bar chart representing all closed, high priority tickets with or without steps 
to reproduce in either the description field or in any of the comments.

As it can be shown in the figure, having steps to reproduce can significantly reduce the time-to-close 
for the ticket. Even though the data collected does not have such many tickets with steps to reproduce 
(39,988 compared to the total number of 238,286 closed tickets), it is still a valuable finding which shows 
that steps to reproduce are indeed a quality factor for software tickets.

What we can infer from this result is that steps to reproduce reduce the communication friction between 
the reporters and the developers - in the case of a bug which is harder to reproduce (e.g. maybe the 
bug occurs only on Linux and the developer is running MacOS, but the reporter did not specify his/her 
operating system in the ticket), the developer might need to contact the reported either directly or 
through commenting on the issue. What this implies is waiting time until the reporter comes back on the 
issue tracking system or sees the notification that he/she received a new message, which subsequently makes 
the ticket remain open for a longer period of time.

A Welch T Test was computed to test the difference between tickets with steps to reproduce 
and those without steps to reproduce. The analysis revealed significant difference with 
$p < 0.01$ with an average of $1596.714$ for tickets with steps to reproduce and an average of 
$2609.142$ for tickets without steps to reproduce.

Thus, the answer to our research question is that the presence of steps to reproduce in tickets 
has a positive influence on the time-to-close. One solution that we propose for maximizing their benefit 
is that issue tracking systems should include hints on the ticket creation form specifying that 
steps to reproduce should be included as developers would be able to fix the bug faster. Moreover, 
issue tracking systems could also automatically add a new system field (like summary or description) 
for any project created and the project maintainers or administrators could make them mandatory for 
when a ticket is created by reporters.
